### 2016-06-01 symbols_definition.tex
Modifications on paper1 to unify the notation of the document

\multicolumn{3}{c}{{\Large \textbf{Upper-case Roman}}} \\
$\mathcal{N}_h(K)$ & Set of interpolation nodes & \\
$\thn$ & finite element mesh & \\
$\thm$ & finite element adaptive mesh at adaptivity step $m$ &\\	
$\vh$ & piecewise polynomial space of discrete solutions (continuous or discontinuous)& \\
$V_h^k$ & piecewise polynomial space of order $k$  &\\
$V_{h,0}$ & piecewise polynomial space with homogeneous Dirichlet boundary conditions  &\\
$\vm$ & piecewise polynomial space of discrete solutions at the $m$ adaptive step & \\

@@

\multicolumn{3}{c}{{\Large \textbf{Upper-case Greek}}}\\
$\Omega$ & domain \\
$\Gamma$  & domain boundary ($\Gamma=\partial\Omega$) & \\
$\Gamma_{\rm in}$ & inflow boundary ($\Gamma_{\rm in} := \{ x \in \partial \Omega: \, \beta(x) \cdot n(x) < 0\}$)\\

>>>>

\multicolumn{3}{c}{{\Large \textbf{Upper-case Roman}}} \\
$\facet$ & facet & \\
$H^\beta(\Omega)$ & Space of solutions of the weak transport problem &\\
& { ($H^\beta(\Omega) := \{ u \in L^2(\Omega): \,  \nabla \cdot (\beta u) \in L^2(\Omega) \}$)}\\
$K$, $K_i$ & elements of the mesh (in Chaper \ref{chap-paper3} they are ordered by convenience of the analysis) & \\
$K^+_\facet$/$K^-_\facet$ & elements that surround facet $\facet$ ($\facet = \partial K^+_\facet\cap K^-_\facet$ ) & \\
$\mathcal{N}_h(K)$ & Set of interpolation nodes & \\
$P_k(\omega)$ & space of complete polynomials of degree $k$ on $\omega$ & \\
$Q_k(\omega)$ & space of polynomials with maximum degree $k$ in $\omega$\\
$\thn$ & finite element mesh & \\
$\thm$ & finite element adaptive mesh at adaptivity step $m$ &\\	
$\vh$ & piecewise polynomial space of discrete solutions (continuous or discontinuous)& \\
$V_h^k$ & piecewise polynomial space of order $k$  &\\
$V_{h,0}$ & piecewise polynomial space with homogeneous Dirichlet boundary conditions  &\\
$\vm$ & piecewise polynomial space of discrete solutions at the $m$ adaptive step & \\

@@

\multicolumn{3}{c}{{\Large \textbf{Upper-case Greek}}}\\
$\Omega$ & domain \\
$\Omega_i$ & macroelement associated to node $x_i$ & \\
$\Gamma$  & domain boundary ($\Gamma=\partial\Omega$) & \\
$\Gamma_{\rm in}$ & inflow boundary ($\Gamma_{\rm in} := \{ x \in \partial \Omega: \, \beta(x) \cdot n(x) < 0\}$)\\
